### 2022-01-08 experiments.tex
figures

@@

For these scenarios, we vary:
\begin{itemize}
    \item the sampling rate of the Plant state, setting it to \SIlist[list-final-separator={, or }]{5;10;20;40;60}{\hertz};
    \item the responsiveness of the Controller, by adding fixed delays of  \SIlist[list-final-separator={, or }]{0;25;50;100}{\milli\second} after the processing of each sample.
\end{itemize}

@@

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable analysis of relevant metrics.  
\Cref{fig:topple:fraction} shows a visualization of the fraction of plants that toppled in each scenario.
These Plants were identified simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value depends on the parametrization of the controller; in this case it corresponds to \SI{0.35}{\radian}.} were marked as ``toppled''.
Next, we showcase \ac{CLEAVE}'s ability to obtain network performance data from the experiments.
\Cref{fig:single:network} shows average latency due to network and processing (excluding synthetic delays) for both single-loop scenarios, and packet losses for the networked single-loop scenario\footnote{Packet losses in the local scenario were, of course, \SI{0}{\percent}.}.

From these results we can already infer interesting consequences for \ac{NCS} deployments on the edge.
For instance, it is clear from \cref{fig:topple:fraction} that network delays can, to a certain extent, be compensated for by increasing the sampling rate of the system.
A corollary of this is that, conversely, at lower network latencies \acp{NCS} are able to stabilize at lower sampling rates.
Adaptive sampling might thus be a straightforward method for optimizing \ac{NCS} resource utilization and energy consumption at the edge.

\begin{figure*}
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_toppled}
        \caption{}%
        \label{fig:topple:fraction}
    \end{subfigure}%
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_rms}
        \caption{}\label{fig:single:rms}
    \end{subfigure}%
    \caption[caption]{
        Stability metrics for the single-loop scenarios.
        \labelcref{fig:topple:fraction} shows the fraction of plants that toppled, per experimental setup.
        \labelcref{fig:single:rms} shows the \ac{RMS} value of the angle for all penduli that did not topple in the single loop scenarios.
        Error bars indicate \SI{95}{\percent} \acp{CI}.
        }%
    \label{fig:single:network}
    \todo[inline]{More focus on this.}
\end{figure*}

@@

% \begin{figure}
%     \centering
%     \begin{subfigure}[h]{\columnwidth}
%         \centering
%         \includegraphics[width=.8\columnwidth]{video_drop_frac}
%         \caption{}\label{fig:video:drop}
%     \end{subfigure}\\%
%     \begin{subfigure}[h]{\columnwidth}
%         \centering
%         \includegraphics[width=.8\columnwidth]{video_rtt}
%         \caption{}\label{fig:video:rtt}
%     \end{subfigure}%
%     \caption{
%         Network metrics for the realistic scenario.
%         Error bars indicate \SI{95}{\percent} \ac{CI} in both plots.
%     }\label{fig:video:network}
% \end{figure}

>>>>

\begin{figure*}[h]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_toppled}
        \caption{}%
        \label{fig:single:topple}
    \end{subfigure}%
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_rms}
        \caption{}\label{fig:single:rms}
    \end{subfigure}%
    \caption[caption]{
        Stability metrics for the single-loop scenarios.
        \labelcref{fig:single:topple} shows the fraction of plants that toppled, per experimental setup.
        \labelcref{fig:single:rms} shows the \ac{RMS} value of the angle for all penduli that did not topple in the single loop scenarios.
        Error bars indicate \SI{95}{\percent} \acp{CI}.
        }%
    \label{fig:single:stability}
    \todo[inline]{More focus on this.}
\end{figure*}

@@

For these scenarios, we vary:
\begin{itemize}
    \item the sampling rate of the Plant state, setting it to \SIlist[list-final-separator={, or }]{10;20;40;60}{\hertz};
    \item the responsiveness of the Controller, by adding fixed delays of  \SIlist[list-final-separator={, or }]{0;25;50}{\milli\second} after the processing of each sample.
\end{itemize}

@@

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable analysis of relevant metrics.  
\Cref{fig:single:stability} shows the results relating to the stability of the plants in the single-loop scenarios:
\cref{fig:single:topple} shows a visualization of the fraction of plants that toppled in each scenario, and \cref{fig:single:rms} shows the average \ac{RMS} amplitude for the penduli angles.

We identify toppled plants simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value depends on the parametrization of the controller; in this case it corresponds to \SI{0.35}{\radian}.} were marked as ``toppled''.

Next, we showcase \ac{CLEAVE}'s ability to obtain network performance data from the experiments.
\Cref{fig:single:rtt} shows average latency due to network and processing (excluding synthetic delays) for both single-loop scenarios.
Packet losses were below \SI{0.2}{\percent} for all parametrizations of the single-loop scenario over the network, and \SI{0}{\percent} for all parametrizations of the local-only setup.

From these results we can already infer interesting consequences for \ac{NCS} deployments on the edge.
For instance, it is clear from \cref{fig:single:stability} that network delays can, to a certain extent, be compensated for by increasing the sampling rate of the system.
A corollary of this is that, conversely, at lower network latencies \acp{NCS} are able to stabilize at lower sampling rates.
Adaptive sampling might thus be a straightforward method for optimizing \ac{NCS} resource utilization and energy consumption at the edge.

@@
